### 2015-07-23 usecase-ares.tex
update ARES text to go with table.

Table~\ref{tab:ares-configs} shows the configurations of ARES that we have packaged.
The rows and columns show architectures, compilers, and MPI versions.
The ARES Spack package supports four different code configurations:
the current and previous production versions, a ``lite'' version that includes
a smaller set of features and dependencies, and a development version.  We 
denote these as C, P, L, and D. Each cell in the table indicates the
ARES configurations built for an architecture, compiler, and MPI combination.
Each configuration requires a slightly different set of dependencies and 
dependency versions, but one common ARES package supports all of them with 
conditional logic on versions and variants.

Altogether, the initial packaging effort for ARES took roughly two months,
half time, for an experienced build engineer. It supports 64 different builds
(4 configurations and 8 architecture-compiler-MPI combinations). Prior to 
using Spack, only the Linux/Intel configurations were automated. The ARES 
team listed a number of key features that enabled the increased automation:
\begin{enumerate}
\item Spack's version tracking and optional dependencies were required to
      build the four configurations with correct libraries;
\item The spec syntax allowed build scripts to concisely test compiler,
      compiler version, and dependency versions: a necessity
      for handling the different architectures;
\item Patching packages for particular platforms was
      necessary to build many packages; and
\item Using a DSL embedded in Python was a significant benefit;
      certain packages required custom scripting to patch.
\end{enumerate}

>>>>

Table~\ref{tab:ares-configs} shows configurations of ARES that the ARES
team tests nightly.  The rows and columns show architectures, compilers, and MPI versions.
The ARES Spack package supports four different code configurations:
the current (C) and previous (P) production versions, a ``lite'' version (L) that includes
a smaller set of features and dependencies, and a development version (D).
Each cell in the table indicates the ARES configurations built for an architecture,
compiler, and MPI combination. Each configuration requires a slightly different
set of dependencies and dependency versions, but one common ARES package supports
all of them with conditional logic on versions and variants.

Altogether, the initial packaging effort for ARES took roughly two months,
half time, for an experienced build engineer. As shown in the table, 32
different configurations have been run using Spack
(some of 4 versions on each of 10 architecture-compiler-MPI combinations).
Prior to using Spack, only Linux/Intel configurations were automated. The ARES 
team listed a number of key features that enabled the increased automation:
\begin{enumerate}
\item Spack's version tracking and optional dependencies were required to
      build the four configurations with correct libraries;
\item The spec syntax allowed build scripts to concisely test compiler,
      compiler version, and dependency versions: a necessity
      for handling the different architectures;
\item Patching packages for particular platforms was
      necessary to build many packages; and
\item Using a DSL embedded in Python was a significant benefit;
      certain packages required custom scripting to patch.
\end{enumerate}
